---
title: "R Notebook"
output: html_notebook
---



```{r}


library(tibble)
library(dplyr)
library(readr)
library(ggplot2)

library(tensorflow)
library(keras)
library(reticulate)
library(devtools)
library(reticulate)
library(zoo)
library(data.table)
library(xts)
library(forecast) #Acf function
library(lubridate)
library(PerformanceAnalytics) # for function kurtosis()
library(tseries)#adf and jb test
library(rugarch)

library(sjPlot)
library(stargazer)

library(broom)
library(purrr) #for test tables

library(lmtest)
library(plyr)

library(texreg)
#if(!require(devtools)) install.packages("devtools")
#devtools::install_github("kassambara/ggpubr")
#install.packages(remotes)
#remotes::install_github("freysimon/TigR")

library(ggpubr)


```

Once the data prep functions are defined, can every code chunk be run independetly to generate the GARCH and LSTM model estimates, tables and plots for each currency and daily or hourly timeframe
path to the local data file, this should be enough for R markdown since it usually recognized its environment
otherwise define fill system path here
coin variable will be used in loops to generate plots and tables
```{r}
#path = "Data/"
path = "D:/Google Drive/MBF/Masterarbeit/Data/"
coin <- c("BTC","ETH","LTC")
start_date <- ymd("2019/6/30")
end_date <- ymd("2022/5/1")
set.seed(123)
options("scipen"=100, "digits"=6) #no scientific not
```




# Data Loading and Preprocessing 
Custom functions for later use to pull the necessary data, preprocess and generate the statistics
```{r}
get_stats <- function(tab){
  df <- data.frame("var"=c("Sample size","Mean","Std","Min","Max","Skewness","Excess kurtosis"),
                 curr=c(nrow(tab),mean(tab),StdDev(tab),min(tab),max(tab),
                        skewness(tab),
                        kurtosis(tab, method = "excess")))
  return (df)
}


#####################################
get_test_stats <- function(tab,lag){
#Ljung box for autocorrelation
l1 <- Box.test(tab, lag = lag, type = "Ljung-Box")
#H0 no autocorrelation 

#augmented dickey fuller test for unit root
adft <- adf.test(tab)
#H0 unit root

# test for non normality with the jarque bera
jbt <- jarque.bera.test(tab)


tab <- map_df(list(l1,jbt,adft), tidy)
tab <- tab[,c("method","statistic","p.value")]
tab[1,1] <- c("Box-Ljung Test")
  return(tab)
}


#######################################
get_h_data <- function(curr){
  dat_h <- read.csv(paste0(path,"Price/Hour/Cryptocompare/",curr,"_price.csv"))
colnames(dat_h) <- c("ts","high","low","open","close","volume")
dat_h$ts <- ymd_hms(dat_h$ts)
  
#xts time format
dat_h <- as.xts(dplyr::select(dat_h, -c(ts)) , order.by = dat_h$ts)

#log returns and vol change
dat_h$ret <- diff(log(dat_h$close))
dat_h$v_chg <- diff(log(dat_h$volume))

dat_h$ret2 <- dat_h$ret^2 #squared returns
dat_h$rv <- rollsum(dat_h$ret2,24,fill=NA,align="right") #24h variance as sum of sqr returns

#remove NA 
dat_h <- na.omit(dat_h)
dat_h <- dat_h[!is.infinite(dat_h$v_chg),]

#match dates
dat_h <- dat_h[index(dat_h)>start_date]
dat_h <- dat_h[index(dat_h)<end_date]
return(dat_h)
}



############################################
get_d_data <- function(curr){
dat_d <- read.csv(paste0(path,"Price/Day/Cryptocompare/",curr,"_price.csv"))
colnames(dat_d) <- c("ts","high","low","open","close","volume")
dat_d$ts <- ymd(dat_d$ts)

dat_d <- as.xts(dplyr::select(dat_d, -c(ts)) , order.by = dat_d$ts)
dat_d$ret <- diff(log(dat_d$close))
dat_d$v_chg <- diff(log(dat_d$volume))

dat_d$ret2 <- dat_d$ret^2 #squared returns

#remove NA 
dat_d <- na.omit(dat_d)
dat_d <- dat_d[!is.infinite(dat_d$v_chg),]

dat_d <- dat_d[index(dat_d)>start_date]
dat_d <- dat_d[index(dat_d)<end_date]

return(dat_d)
}

##########################################
get_fun_dat <- function(curr){
  #FTX
  dat_funftx <- read.csv(paste0(path,"Funding/FTX_",curr,"_funding.csv"))
  dat_funftx <- dat_funftx[,c("rate","ts")]
  colnames(dat_funftx) <- c("ftx","ts")
  dat_funftx$ts <- as.POSIXct(dat_funftx$ts,format="%d.%m.%Y %H:%M")
  #dat_funftx$ts <- lubridate::dmy_hms(dat_funftx$ts)
  
  #BINANCE
  dat_funbin <- read.csv(paste0(path,"Funding/BINANCE_",curr,"_funding.csv",sep = ""))
  dat_funbin <- dat_funbin[,c("ï..Time","Funding.Rate")]
  colnames(dat_funbin) <- c("ts","bin")
  dat_funbin$bin <- as.numeric(sub("%", "", dat_funbin$bin))/100 #convert from pct string to number
  dat_funbin$ts <- as.POSIXct(dat_funbin$ts,format="%d.%m.%Y %H:%M")
  bin_fun_start <- min(dat_funbin$ts)
  
  #BITMEX
  dat_funbit <- read.csv(paste0(path,"Funding/BITMEX_",curr,"_funding.csv"))
  dat_funbit <- dat_funbit[,c("timestamp","funding")]
  colnames(dat_funbit) <- c("ts","bit")
  dat_funbit$ts <- as.POSIXct(dat_funbit$ts,format="%Y-%m-%d %H:%M")
  
  #merge binance and bitmex
  dat_fun <- merge(dat_funbit,dat_funbin,on="ts", all = TRUE)
  #divide by eight to get to hourly rates
  dat_fun[,c("bin","bit")] <- dat_fun[,c("bin","bit")]/8
  #backfill the NA timeseries
  dat_fun$bin <- nafill(dat_fun$bin, type = "locf")
  
  #merge with FTX
  dat_fun <- merge(dat_fun,dat_funftx, on="ts",all=TRUE)
  
  
  #rowsums, but if all entries are NA, keep the NA value instead of replacing it with 0
  dat_fun$funding <- rowSums(dat_fun[,c("ftx","bin","bit")], na.rm=TRUE) * ifelse(rowSums(is.na(dat_fun[,c("ftx","bin","bit")])) == ncol(dat_fun[,c("ftx","bin","bit")]),NA,1)
  #divide by number of exchanges that contributed to the sum
  dat_fun$funding <- dat_fun$funding / rowSums(!is.na(dat_fun[,c("bit","bin","ftx")]))
  
  #remove NA funding
  dat_fun <- dat_fun[!is.na(dat_fun$funding),]
  
  #remove NA in time
  dat_fun <- dat_fun[!is.na(dat_fun$ts),]
  
  dat_fun$funding <- dat_fun$funding*100
  
  #xts format
  dat_fun <- as.xts(dat_fun[,-1],order.by = dat_fun[,1])

  #start end
  dat_fun <- dat_fun[index(dat_fun)>start_date]
  dat_fun <- dat_fun[index(dat_fun)<end_date]
  return(dat_fun)
}


####################
get_fee_dat <- function(curr){
  
dat_fee <- read.csv(paste0(path,"Fee/",curr,"_fee.csv"))
head(dat_fee)
dat_fee <- dat_fee[,c("time","FeeMeanUSD")]
colnames(dat_fee) <- c("ts","fee")
dat_fee$ts <- lubridate::ymd_hms(dat_fee$ts)
dat_fee <- xts(dat_fee[,-1],order.by = dat_fee[,1])
colnames(dat_fee) <- "fee"

#start end
dat_fee <- dat_fee[index(dat_fee)>start_date]
dat_fee <- dat_fee[index(dat_fee)<end_date]

#normalize by price of currency
# get daily data
dat_d <- get_d_data(curr)
dat_fee$fee <- dat_fee$fee/dat_d$close * 100

#na
dat_fee <- na.omit(dat_fee)
return(dat_fee)
}


##############################################
get_social_dat <- function(curr){
  #load and format the data
dat_social <- read.csv(paste0(path,"Social/Hour/",curr,"_social.csv"))
head(dat_social)
colnames(dat_social) <- c("ts","reddit_c","reddit_p","reddit_sub")
dat_social$ts <- lubridate::dmy_hm(dat_social$ts)
dat_social <- xts(dat_social[,-1],order.by = dat_social[,1])

#start end
dat_social <- dat_social[index(dat_social)>start_date]
dat_social <- dat_social[index(dat_social)<end_date]

#normalize by subscriber count
dat_social$reddit_c_n <- dat_social$reddit_c / dat_social$reddit_sub * 100
    dat_social$reddit_p_n <- dat_social$reddit_p / dat_social$reddit_sub * 100
return(dat_social)
}
```


function to extract GARCH parameters
```{r}
extract.rugarch <- function(fit, 
                            include.rsquared = F, include.loglike = TRUE, include.aic = TRUE, include.bic = TRUE) {
  
  # extract coefficient table from fit:
  coefnames <- rownames(as.data.frame(fit@fit$coef))
  coefs <- fit@fit$coef
  se <- as.vector(fit@fit$matcoef[, c(2)])
  pvalues <-  as.vector(fit@fit$matcoef[, c(4)])       # numeric vector with p-values
  
  # create empty GOF vectors and subsequently add GOF statistics from model:
  gof <- numeric()
  gof.names <- character()
  gof.decimal <- logical()
  if (include.rsquared == TRUE) {
    r2 <-  1 - (var(fit@fit$residuals) / var(y))
    gof <- c(gof, r2)
    gof.names <- c(gof.names, "R^2")
    gof.decimal <- c(gof.decimal, TRUE)
  }
  if (include.loglike == TRUE) {
    loglike <- fit@fit$LLH
    gof <- c(gof, loglike)
    gof.names <- c(gof.names, "Log likelihood")
    gof.decimal <- c(gof.decimal, TRUE)
  }
  if (include.aic == TRUE) {
    aic <- infocriteria(fit)[c(1)]
    gof <- c(gof, aic)
    gof.names <- c(gof.names, "AIC")
    gof.decimal <- c(gof.decimal, TRUE)
  }
  
  if (include.bic == TRUE) {
    bic <- infocriteria(fit)[c(2)]
    gof <- c(gof, bic)
    gof.names <- c(gof.names, "BIC")
    gof.decimal <- c(gof.decimal, TRUE)
  }

  d_inf <- data.frame("Criteria"=gof.names,"Value"=gof)
  tr <- data.frame("Parameter"=coefnames,"Estimate"=coefs,"Standard Error"=se,"P.value"=pvalues)
  return(list(tr,d_inf))
}



```

get significance stars
```{r}
#get significance starts
stars.pval <- function(x){
  stars <- c("***", "**", "*", " ")
  var <- c(0, 0.01, 0.05, 0.10, 1)
  i <- findInterval(x, var, left.open = T, rightmost.closed = T)
  stars[i]
}
```


Load and analyze price and volume data,generate plots and tables
time frame/period and currency can be selected

```{r}
curr = "ETH"
t_period = "hour"


df_all <- data.frame()

for (i in coin) {
  curr = i

  if (t_period == "day") {
  dat_price <- get_d_data(curr)
  }
  if (t_period == "hour"){
  dat_price <- get_h_data(curr)
  }


############
# explore the data
############

# #partial autocorrelation
# q <- forecast::ggtsdisplay(dat_price$ret,lag.max=30)
# q <- q + theme(panel.background = element_rect(fill = 'white', colour = 'black'))
# q <- q + ggtitle(curr) + ggtitle(curr)
# q
# ggsave(q, filename = paste0(path,"Plots/",curr,"_pAcF_daily.png"),height = 2.5, width = 9)  

#partial autocorrelation returns
q <- forecast::ggtsdisplay(dat_price$ret,lag.max=30)
q <- q + theme(panel.background = element_rect(fill = 'white', colour = 'black'))
q <- q + ggtitle(" ") + labs(y= "PACF Returns")
q
#ggsave(q, filename = paste0(path,"Plots/",curr,"_pAcF_ret_hourly.png"),height = 2.5, width = 9)  

#partial autocorrelation squared returns
p <- forecast::ggtsdisplay(dat_price$ret2,lag.max=30)
p <- p + theme(panel.background = element_rect(fill = 'white', colour = 'black'))
p <- p + ggtitle(curr) + labs(y= "PACF Returns^2")
p
#ggsave(p, filename = paste0(path,"Plots/",curr,"_pAcF_ret2_hourly.png"),height = 2.5, width = 9)  

pq_plot <- ggarrange(p, q, heights = c(2, 2),
          ncol = 2, nrow = 1,align = "h")
print(pq_plot)
ggsave(pq_plot, filename = paste0(path,"Plots/",curr,"_",t_period,"_daily_pacf_all.png"),height = 2, width = 9)



#test statistics
tab <- get_test_stats(dat_price$ret,lag=10)
#assign(paste0("tab_test",curr),tab)
colnames(tab) <- c("var",curr,"pvalue")
#summaty stats
df <- get_stats(dat_price$ret)
colnames(df) <- c("var",curr)
df$pvalue <- NA
df = join(df,tab,type="full")
df <- transform(df, stars = stars.pval(df$pvalue))
df$pvalue <- NULL
if (dim(df_all)[1] == 0){
  df_all <- df
  }else{
 df_all <- join(df_all,df,by="var") 
}
}





#df_all <- transform(df_all, stars = stars.pval(df_all$pvalue))

#colnames(df_all) <- c(" ",coin)
tab_df(df_all,digits = 4, 
          file = paste0(path,"Tables/",t_period,"summary_stats.doc"))



```


plot the funding data

```{r}
#coin <- c("BTC","ETH","LTC")
#l_fund <- list() #ggplots in list not working
#i = "LTC"
for (i in coin) {
  curr = i
  dat_fun <- get_fun_dat(curr)
  
  #create plot
  fplot <- autoplot(dat_fun[,("funding")]) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(panel.background = element_rect(fill = 'white', colour = 'black')) + labs(y= "Funding rate (%/h)", x = "Date") + ggtitle(curr) 
  print(fplot)
  #ggsave(fplot, filename = paste0("Plots/",curr,".png"),height = 2.5, width = 9)
  #build seperate variables for comboplot
  assign(paste0("fplot",curr),fplot)
  #l_fund[i] <- fplot
}
fplot_all <- ggarrange(fplotBTC, fplotETH, fplotLTC, heights = c(2, 2, 2),
          ncol = 1, nrow = 3,align = "v")

fplot_all
ggsave(fplot_all, filename = paste0(path,"Plots/","all_f",".png"),height = 7, width = 9)
hist(dat_fun$funding)

```



Transaction fee
```{r}
#curr <- "ETH"

for (i in coin) {
  curr = i
dat_fee <- get_fee_dat(curr)


#adf test
adf.test(dat_fee$fee)

#create plot
  fee_plot <- autoplot(dat_fee) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(panel.background = element_rect(fill = 'white', colour = 'black')) + labs(y= "avg Transaction Fee (%)", x = "Date") + ggtitle(curr) 
  #print(fee_plot)
  fee_plot
  assign(paste0("feeplot",curr),fee_plot)
  #ggsave(fee_plot, filename = paste0(path,"Plots/",curr,"_fee.png"),height = 2, width = 9)
  hist(dat_fee)
  dat_fee$fee_chg <- diff(log(dat_fee$fee))
  #na
  dat_fee <- na.omit(dat_fee)
  autoplot(dat_fee$fee_chg)
}
fplot_all <- ggarrange(feeplotBTC, feeplotETH, feeplotLTC, heights = c(2.5, 2.5, 2.5),
          ncol = 1, nrow = 3,align = "v")

fplot_all
ggsave(fplot_all, filename = paste0(path,"Plots/","all_fees",".png"),height = 7, width = 9)

```


Reddit Data
```{r}
#curr <- "BTC"
for (i in coin){
#load and format the data
  curr = i
dat_social <- get_social_dat(curr)


#create plot
  social_plotc <- autoplot(dat_social[,1]) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(panel.background = element_rect(fill = 'white', colour = 'black')) + labs(y= "Reddit Comments per Hour", x = "Date") + ggtitle(" ") 
  print(social_plotc)
  #ggsave(social_plotc, filename = paste0("Plots/",curr,"_social_c.png"),height = 2.5, width = 9)

    social_plotp <- autoplot(dat_social[,2]) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(panel.background = element_rect(fill = 'white', colour = 'black')) + labs(y= "Reddit Posts per Hour", x = "Date") + ggtitle(curr) 
  print(social_plotp)
  #ggsave(social_plotp, filename = paste0("Plots/",curr,"_social_p.png"),height = 2.5, width = 9)  

  social_plot_all <- ggarrange(social_plotp, social_plotc, heights = c(0.5),
          ncol = 2, nrow = 1)
  social_plot_all
  ggsave(social_plot_all, filename = paste0(path,"Plots/",curr,"_social_all_p.png"),height = 2, width = 9)  
}
```

summary stats for the external regressors
```{r}
curr <- "BTC"
t_period <- "hour"
df_all <- data.frame()
for (i in coin) {
 curr=i
#### get the data
dat_d <- get_d_data(curr)
dat_h <- get_h_data(curr)
dat_social <- get_social_dat(curr)
dat_fun <- get_fun_dat(curr)
dat_fee <- get_fee_dat(curr)
####
dat_stats <- prep_h_data(dat_h,dat_fee,dat_fun,dat_social)
#test statistics
tab <- get_test_stats(dat_stats[,3],lag=10)
#assign(paste0("tab_test",curr),tab)
colnames(tab) <- c("var",curr,"pvalue")
#summaty stats
autoplot(dat_stats$reddit_p_n)
df <- get_stats(dat_stats[,3])
colnames(df) <- c("var",curr)
df$pvalue <- NA
df = join(df,tab,type="full")
df <- transform(df, stars = stars.pval(df$pvalue))
df$pvalue <- NULL
if (dim(df_all)[1] == 0){
  df_all <- df
  }else{
 df_all <- join(df_all,df,by="var") 
}
}
tab_df(df_all, digits = 4)
```


Simple GARCH model with no external regressors

```{r}
curr = "BTC"
out_sample_d = round(0.35*nrow(dat_d)) #35% of the data are used out of sample
out_sample_h = round(0.35*nrow(dat_h)) #35% of the data are used out of sample

#### get the data
dat_d <- get_d_data(curr)
dat_h <- get_h_data(curr)
dat_social <- get_social_dat(curr)
dat_fun <- get_fun_dat(curr)
dat_fee <- get_fee_dat(curr)
####



#Garch 1,1 model with zero mean
garchspec <- ugarchspec(
  mean.model = list(armaOrder = c(0,0)),
  variance.model =  list(model = "sGARCH", garchOrder = c(1, 1)),
  distribution.model = "std")

garchfit <- ugarchfit(data = dat_d$ret,
                      spec = garchspec,
                      out.sample = out_sample_d)

garchfit

#forecast
# spec = getspec(garchfit);
# setfixed(spec) <- as.list(coef(garchfit));
# forecast = ugarchforecast(spec, n.ahead = 1, n.roll = 100, data = dat_d$ret[100:300], out.sample = 100)
forecast = ugarchforecast(garchfit,n.ahead = 1, n.roll = out_sample_d,out.sample = out_sample_d)

####
#compare forecast to target
dat_rv_d <- apply.daily(dat_h$ret2, FUN = sum)
index(dat_rv_d) <- as.Date(index(dat_rv_d))
colnames(dat_rv_d) <- "rv"



g_fc <- sigma(forecast)
g_fc <- t(g_fc)

#g_fc <- data.frame(g_fc)
#g_fc$T.1 <- lag(g_fc$T.1) #lag to have the prediction on prediction day
#g_fc <- as.xts(g_fc)
#index(g_fc) <- as.Date(index(g_fc))


if (t_period == "day"){
g_fc <- data.frame(g_fc)
g_fc$date <- rownames(g_fc)
rownames(g_fc) <- NULL
g_fc$T.1 <- lag(g_fc$T.1,n=1) #lag to have the prediction on prediction day
g_fc <- na.omit(g_fc)
g_fc <- as.xts(g_fc$T.1, order.by = ymd(g_fc$date))
g_fc <- merge(g_fc,dat_data_d$rv)
}


g_fc <- merge(g_fc,dat_rv_d)
g_fc <- na.omit(g_fc)

#get error statistics
g_acc <- accuracy(as.numeric(g_fc$T.1),as.numeric(g_fc$rv))
g_acc

# tab <- map_df(list(g_acc,g_acc), tidy)
# tab <- tab[,c("method","statistic","p.value")]
# tab[1,1] <- c("Box-Ljung Test")
#   return(tab)
# }


#plot vs prediction
  p <- ggplot(g_fc, aes(x=index(g_fc), y = rv)) + geom_point( colour = "blue", size = 0.3,alpha=0.5)
  p <- p + geom_point(aes(y = g_fc$T.1^2) ,colour = "red", size = 0.3 ,alpha=0.5) 
  p <- p + theme(panel.background = element_rect(fill = 'white', colour = 'black')) + 
    labs(y= "RV", x = "Date") + ggtitle(curr) 
  p <- p +  scale_x_date(date_breaks = "3 month",date_labels = "%Y %b")
  p 
  ggsave(p, filename = paste0(path,"Plots/",curr,"_simple_garch.png"),height = 3, width = 9)  

  #scatterplot remove one outlier
  g_fc <- g_fc[which(!g_fc$rv==max(g_fc$rv)),] 
  ggplot(g_fc, aes(x=T.1^2, y=rv)) +
  geom_point(size=2, shape=23)

#extract garch params and print table  
g_tab <- extract.rugarch(garchfit)

tab_dfs(list(g_tab[[1]],g_tab[[2]]),title=c(curr,curr),
        file = paste0(path,"Tables/",curr,"simple_garch.doc"))



```

Grid search for optimal parameter estimation
```{r, eval = FALSE}
#grid search over different parameters
final.aic <- Inf
final.order <- c(0,0,0,0)
for (i in 0:0) for (j in 0:0) for (k in 1:4) for(l in 1:4) {
  garchspec <- ugarchspec(
    mean.model = list(armaOrder = c(i,j)),
    variance.model =  list(model = "sGARCH", garchOrder = c(k, l)),
    distribution.model = "std")
  garchfit <- ugarchfit(data = dat_d$ret,
                        spec = garchspec,
                        out.sample = out_sample_d)

  if (garchfit@fit$convergence == 0){
    current.aic <- infocriteria(garchfit)[1]
    if (current.aic*0.98 < final.aic) #1% improvement
      final.aic <- current.aic
    final.order <- c(i, j, k, l)
  }
}
```


helper function to prep the hourly data
```{r}
prep_h_data <- function(dat_h,dat_fee,dat_fun,dat_social){

dat_data <-  merge(dat_h[,c("rv","ret","ret2","v_chg")], dat_fee$fee, dat_fun[,"funding"],
                  dat_social[,c("reddit_c_n","reddit_p_n")])

#cut of leading and trailing NA in the fee chg for the interpolation 
dat_data <- dat_data[min(which(!is.na(dat_data$fee))):max(which(!is.na(dat_data$fee))),]
dat_data$fee <- na.spline(dat_data[,c("fee")], xout = index(dat_data))
#take log diff
dat_data$fee <- diff(log(dat_data$fee))

#nas
dat_data <- na.omit(dat_data)
return (dat_data)
}
```

helper function to prep daily data
```{r}
prep_d_data <- function(dat_d,dat_fee,dat_fun,dat_social) {
dat_data_d <- dat_d[,c("ret","ret2","v_chg")]

#transform daily
col_sum <- function(x, na.rm = FALSE) {
  apply(x, 2, sum, na.rm = na.rm)
}
#data is summed including end of day 23:00, index is matched to daily price series
dat_social_d = apply.daily(dat_social, FUN = col_sum)
index(dat_social_d) <- as.Date(index(dat_social_d))
dat_data_d <- merge(dat_data_d,dat_social_d)

dat_funding_d <- apply.daily(dat_fun$funding, FUN = sum)
index(dat_funding_d) <- as.Date(index(dat_funding_d))
dat_data_d <- merge(dat_data_d,dat_funding_d)

dat_rv_d <- apply.daily(dat_h$ret2, FUN = sum)
index(dat_rv_d) <- as.Date(index(dat_rv_d))
colnames(dat_rv_d) <- "rv"


dat_data_d <- merge(dat_data_d,dat_rv_d)
dat_data_d <- merge(dat_data_d,dat_fee)
dat_data_d <- na.omit(dat_data_d)

dat_data_d <- dat_data_d[,c("rv","v_chg","reddit_c_n","reddit_p_n","funding","ret","fee")]

head(dat_data_d)
dat_data_d$ret2 <- dat_data_d$ret^2
return(dat_data_d)
}
```

correlation analysis
```{r}
curr = "BTC"
t_period <- "hour" #day #choose for the model forecast, to adjust the model forecast length, dataselection and 
method <- "pearson"
df_all <- data.frame() #collect the tables

l_cor <- list()
# get_garch <- function(curr){
for (i in coin) {
    curr = i
#### get the data
dat_d <- get_d_data(curr)
dat_h <- get_h_data(curr)
dat_social <- get_social_dat(curr)
dat_fun <- get_fun_dat(curr)
dat_fee <- get_fee_dat(curr)
####
###########################
if (t_period == "day"){
garch_data <- prep_d_data(dat_d = dat_d,dat_fee = dat_fee,dat_fun=dat_fun,dat_social)
}

if (t_period == "hour"){
garch_data <- prep_h_data(dat_h,dat_fee,dat_fun,dat_social)
}
##########################
# #correlation matrix
dat_corr <- as.data.frame(garch_data[,-1])
#dat_corr$date <- rownames(dat_corr)
rownames(dat_corr) <- NULL
dat_corr[,c("v_chg","fee","funding","reddit_c_n","reddit_p_n")] <- 
lag(dat_corr[,c("v_chg","fee","funding","reddit_c_n","reddit_p_n")])
dat_corr <- na.omit(dat_corr)
dat_corr$ret <- NULL
head(dat_corr)
dat_corr <- dat_corr[,c("ret2","v_chg","fee","funding","reddit_p_n","reddit_c_n")]
colnames(dat_corr) <- c("r2","Volume","Fee","Funding","RedditCom","RedditPost")
tab_corr(dat_corr,corr.method = c(method),fade.ns = F,title = curr,
         file = paste0(path,"/Tables/","corr_",curr,t_period,".doc"))
l_cor[[i]] <- dat_corr

}




# name = "LTC"
tab_corr(l_cor[[name]],corr.method = c(method),fade.ns = F,title = name)
tab_corr(l_cor[[name]],corr.method = c(method),fade.ns = F,title = name,
 file = paste0(path,"/Tables/","corr_",name,t_period,".doc"))
# cor(dat_corr)
# plot(dat_corr$r2,dat_corr$Fee)
# stat_cor(
#   mapping = NULL,
#   data = dat_corr[,c(1:2)],
#   method = "spearman"
# )

#currency correlation 
h_rets <- lapply(coin, get_h_data)
h_rets <- merge(h_rets[[1]],h_rets[[2]],h_rets[[3]], all.x=TRUE, all.y=TRUE)
h_rets <- h_rets[,c("ret","ret.1","ret.2")]
colnames(h_rets) <- coin
tab_df(as.data.frame(cor(h_rets),method = method),file=paste0(path,"/Tables/","currency_corr_",method,t_period,".doc"),show.rownames = T)

ll <- lapply(l_cor,FUN=cor,method=method)
df <- as.data.frame(do.call(rbind,unname(ll)))
library(psych)
corr.test(l_cor$BTC, method = method)
?corr.test
ll$BTC
#tab_df(df,show.rownames = T)
tab_df(df,show.rownames = T,file=paste0(path,"/Tables/","all_corr_",method,t_period,".doc"))


# ggscatter(l_cor$BTC, x = "r2", y = "Fee",
#           color = "blue", cor.coef = TRUE, 
#           cor.method = "spearman",
#           xlab = "Brent (TL)", ylab = "Gasoline (TL)")

# for (name in names(l_cor)) {
#     print(name)
#     print(l_cor[[name]])
#         tab_corr(l_cor[[name]],corr.method = c("pearson"),fade.ns = F,title = curr,
#          file = paste0(path,"/Tables/","corr_",name,t_period,".doc"))
```


Garch with additional parameters
```{r}
out_sample_d = 0.35 #35% of the data are used out of sample dor daily timeframe
out_sample_h = 0.35  #35% of the data are used out of sample for hourly time frame

curr = "BTC"
t_period <- "day" #day #choose for the model forecast, to adjust the model forecast length, dataselection and 
#calculation of the forecast
variab <- "full" #rets #full
df_all <- data.frame() #collect the tables

# get_garch <- function(curr){
for (i in coin) {
    curr = i
#### get the data
dat_d <- get_d_data(curr)
dat_h <- get_h_data(curr)
dat_social <- get_social_dat(curr)
dat_fun <- get_fun_dat(curr)
dat_fee <- get_fee_dat(curr)
####
###########################


if (t_period == "day"){
garch_data <- prep_d_data(dat_d = dat_d,dat_fee = dat_fee,dat_fun=dat_fun,dat_social)
out_sample <- round(out_sample_d*nrow(dat_d))
}

if (t_period == "hour"){
garch_data <- prep_h_data(dat_h,dat_fee,dat_fun,dat_social)
out_sample <- round(out_sample_h*nrow(dat_h))
}



if (variab == "full"){

# garch_data <- as.data.frame(garch_data)
# rownames(garch_data) <- NULL
# garch_data[,c("v_chg","fee","funding","reddit_c_n","reddit_p_n")] <- 
# lag(garch_data[,c("v_chg","fee","funding","reddit_c_n","reddit_p_n")])
garch_data <- na.omit(garch_data)
# nrow(garch_data)
#create external regressors
regs <- subset(garch_data, select=c(v_chg,fee,funding,reddit_c_n,reddit_p_n))
#regs <- subset(garch_data, select=c(fee))
regs <- data.matrix(regs)
regs <- lag(regs)
regs <- na.omit(regs)

garchspec <- ugarchspec(
  mean.model = list(armaOrder = c(0,0)),
  variance.model =  list(model = "sGARCH", garchOrder = c(1, 1), external.regressors = regs),
  distribution.model = "std")
}

if (variab == "rets") {
  garchspec <- ugarchspec(
  mean.model = list(armaOrder = c(0,0)),
  variance.model =  list(model = "sGARCH", garchOrder = c(1, 1)),
  distribution.model = "std")
}


garchfit <- ugarchfit(data = garch_data$ret,
                      spec = garchspec,resume_with_solver = "hybrid",
                      out.sample = out_sample) 



#forecast
if (t_period=="hour"){
forecast = ugarchforecast(garchfit,n.ahead = 24, n.roll = out_sample,out.sample = out_sample)
}
if (t_period=="day"){
forecast = ugarchforecast(garchfit,n.ahead = 1, n.roll = out_sample,out.sample = out_sample)
}

g_fc <- sigma(forecast)
g_fc <- t(g_fc)
g_fc <- g_fc^2 #squared to match rv

# ###day####
if (t_period == "day"){
g_fc <- data.frame(g_fc)
g_fc$date <- rownames(g_fc)
rownames(g_fc) <- NULL
g_fc$T.1 <- lag(g_fc$T.1,n=1) #lag to have the prediction on prediction day
g_fc <- na.omit(g_fc)
g_fc <- as.xts(g_fc$T.1, order.by = ymd(g_fc$date))
g_fc <- merge(g_fc,garch_data$rv)
}
##intraday
if (t_period == "hour"){
g_fc <- rowSums(g_fc)
g_fc <- data.frame(g_fc)
g_fc$date <- rownames(g_fc)
rownames(g_fc) <- NULL
g_fc$g_fc <- lag(g_fc$g_fc,n=24) #lag to have the prediction 24h later
g_fc <- na.omit(g_fc)
#rownames(g_fc) <- ymd_hms(rownames(g_fc))
g_fc <- as.xts(g_fc$g_fc,order.by = ymd_hms(g_fc$date) )
g_fc <- merge(g_fc,dat_h$rv)
}


g_fc <- na.omit(g_fc)
colnames(g_fc) <- c("pred","rv")
#get mean squared error
g_acc <- accuracy(as.numeric(g_fc[,1]),as.numeric(g_fc[,2]))
g_acc<- data.frame(t(g_acc))
g_acc$Parameter <- rownames(g_acc)
colnames(g_acc) <- c("Estimate","Parameter")

#plot vs prediction
  p <- ggplot(g_fc, aes(x=index(g_fc), y = rv)) + geom_line( colour = "blue", size = 0.2,alpha=0.3)
  p <- p + geom_point(aes(y = g_fc$pred) ,colour = "red", size = 0.1 ,alpha=0.2) 
  p <- p + theme(panel.background = element_rect(fill = 'white', colour = 'black')) + 
    labs(y= "RV", x = "Date") + ggtitle(paste0(curr," GARCH"))
  #p <- p +  scale_x_date(date_breaks = "3 month",date_labels = "%Y %b")
  print(p) 
  
  ggsave(p, filename = paste0(path,"Plots/",curr,"_",t_period,"_",variab,"_garch.png"),height = 2, width = 9)  
  
  
#extract garch params and print table  #"ar1","ma1","ar1","ar2","m_v_chg","m_fee","m_funding", "m_reddit_c_n","m_reddit_p_n",
g_tab <- extract.rugarch(garchfit)
if (variab == "full"){
g_tab[[1]]$Parameter <- c("mu","omega","alpha1", "beta1", "v_chg","fee","funding", "reddit_c_n","reddit_p_n","shape")
}

if (variab == "ret"){
g_tab[[1]]$Parameter <- c("mu","omega","alpha1", "beta1", "shape")
}


df <- tab_dfs(list(g_tab[[1]],g_tab[[2]]),title=c(curr,curr),digits=6)
df


#add significance stars
g_tab[[1]] <- transform(g_tab[[1]], stars = stars.pval(g_tab[[1]]$P.value))
g_tab[[1]] <- g_tab[[1]][,c("Parameter","Estimate","stars")]
colnames(g_tab[[2]]) <- c("Parameter","Estimate")
g_tab[[1]] <- bind_rows(g_tab[[1]],g_tab[[2]])
g_tab[[1]] <- bind_rows(g_tab[[1]],g_acc)
#g_tab[[1]] <- rbind(c("MeanModel"," "," "),g_tab[[1]])
#g_tab[[1]] <- rbind(g_tab[[1]][1:7,],c("VarianceModel"," "," "),g_tab[[1]][-(1:7),])
g_tab[[1]]$Estimate <- as.numeric(g_tab[[1]]$Estimate)

df <- g_tab[[1]]
colnames(df) <- c("Parameter",curr," ")

if (dim(df_all)[1] == 0){
  df_all <- df
  }else{
 df_all <- join(df_all,df,by="Parameter") 
  }



# as.numeric(g_tab[[1]]$Estimate)
# tab_df(g_tab[[1]],col.header = c(" ",curr," "),digits = 4)
#         file = paste0(path,"Tables/",curr,"_",t_period,"_",variab,"_garch.doc"))


}


#tab_df(df_all,col.header = c(" ",curr," "),digits = 6)
tab_df(df_all,col.header = c(" ",curr," "),digits = 5,
        file = paste0(path,"Tables/","all","_",t_period,"_",variab,"_garch.doc"))



# return(g_tab[[1]])
# }
# df_garch <- lapply(coin,get_garch)
# rind_rows(df_garch, .id = "Parameter")
# tab_dfs(df_garch)
# do.call("rbind",df_garch)
# merge(unlist(df_garch), by =0)
# cbindlist(df_garch)
# df <- Reduce(
#     function(x, y) join(x, y, by = "Parameter"),
#     lapply(df_garch, function(x) { x$id <- rownames(x); x }))
# df
# tab_df(df,digits=4)
# sjp.frq(residuals(garchfit))
# plot_frq(as.data.frame(residuals(garchfit)), type = "line")
# hist(residuals(garchfit))
# ??sjp.frq
# ?tab_model
# ?tab_df
```


Generator function for the LSTM model. This function takes in predefined lookback back periods, prediction periods and generates batches to feed into the model. 
Keras understands inputs directly from the function, thus the data is generated on the fly and RAM is saved. 
```{r Generators}
generator <- function(data,
                      lookback,
                      delay,
                      min_index,
                      max_index,
                      batch_size,
                      step) {
  if (is.null(max_index))
    max_index <- nrow(data) - delay - 1
  i <- min_index + lookback
  function() {
     {
      if (i + batch_size >= max_index)
        i <<- min_index + lookback
      rows <- c(i:min(i + batch_size - 1, max_index))
      i <<- i + length(rows)
    }
    samples <- array(0, dim = c(length(rows),
                                lookback / step,
                                dim(data)[[-1]]))
    targets <- array(0, dim = c(length(rows)))
    
    for (j in 1:length(rows)) {
      indices <- seq(rows[[j]] - lookback, rows[[j]] - 1,
                     length.out = dim(samples)[[2]])
      samples[j, , ] <- data[indices, ]
      targets[[j]] <- data[rows[[j]] + delay, 1]
    }
    list(samples, targets)
  }
}

```

Variable generator function, used to get all combinations of variables
```{r}

# variables = colnames(data)[-1]
# n = 6
# combinations = lapply(1:n, function(x)combn(1:n, x))
# formulas = lapply(combinations, function(y){
#   apply(y, 2, function(x){
#     paste(paste(variables[x], collapse = ","), sep=",")
#   })
# })
# 
# formulas = lapply(combinations, function(y){
#   apply(y, 2, function(x){
#     paste(variables[x],  sep=",")
#   })
# })
# formulas = unlist(formulas)
# data[,unlist(strsplit(formulas[10],split = ","))]
# unlist(strsplit(formulas[10],split = ","))
# lapply(formulas,strsplit,split=",")
# strsplit(formulas, split = ",")
# library(stringr)
# as.vector(str_split_fixed(formulas, pattern = ",", n = nchar(formulas)))
```


Data preprocessing

Currency, dataset and time period can be selected
"curr" selects one of the three cryptocurrencies
"hour" is for the intraday timeframe, while "day" for the daily timeframe
"rets" uses only return data, while "full" uses full set

```{r}
curr = "BTC"
t_period = "day" #day #hour
variab <- "rets" #rets # rets uses only return data, while full uses full set
step <- 1
batch_size <- 200
train_split <- 0.45 #45% of data is used
val_split <- 0.20 #20% validation
#df_all <- data.frame()
```


```{r}
df_all <- data.frame() #for some reason teh tables dont get saved in the loop, catch in dataframe, print later
for (i in coin) {#for (j in c("hour")) { #
#### get the data
  curr = i
  # t_period = j
  # print(i)
  # print(j)
  
dat_d <- get_d_data(curr)
dat_h <- get_h_data(curr)
dat_social <- get_social_dat(curr)
dat_fun <- get_fun_dat(curr)
dat_fee <- get_fee_dat(curr)
####



if (t_period=="hour"){
dat_data <- prep_h_data(dat_h = dat_h,dat_fee = dat_fee,dat_fun = dat_fun,dat_social = dat_social)
}
if (t_period=="day"){
dat_data <- prep_d_data(dat_d = dat_d,dat_fee = dat_fee,dat_fun = dat_fun,dat_social = dat_social)
}
#select vars
if (variab == "full") {
data <- data.matrix(dat_data[,c("rv","ret","v_chg","reddit_c_n","reddit_p_n","fee","funding")])

head(data)
}
if (variab == "rets") {
data <- data.matrix(dat_data[,c("rv","ret")])
}






if (t_period == "hour"){
  delay <- 24
  lookback <- 48
}
if (t_period == "day"){
  delay <- 1
  lookback <- 2
}


#variables <- c("rv","ret")
#dat <- run_lstm(variables)
#dat_all <- lapply(formulas[10:12],run_lstm)



##################################################

#train test split for normalization
period_train <- train_split*nrow(data)
data_train <- data[1:(train_split*nrow(data)),]
#get train mean and sd
mean_dat <- apply(data_train, 2, mean)
std_dat <- apply(data_train, 2, sd)
data <- scale(data, center = mean_dat, scale = std_dat)


# #scale minmax
# max_dat <- apply(data_train,2,max)
# min_dat <- apply(data_train,2,min)
# data <- sweep(data,2,min_dat,FUN = "-")
# data <- sweep(data,2,(max_dat-min_dat),FUN = "/")

#validation length
val_start <- period_train+1
val_end <- (train_split+val_split)*nrow(data)

#test length
test_start <- val_end+1
test_end <- min(test_start+period_train*1,nrow(data))

#steps
val_steps <- (val_end - period_train+1 - lookback) / batch_size
train_steps <- period_train / batch_size

#start and end dates
val_start_date <- rownames(data)[val_start]
test_start_date <- rownames(data)[test_start]

#define generators
train_gen <- generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 1,
  max_index = period_train,
  step = step,
  batch_size = batch_size)

val_gen = generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = val_start,
  max_index = val_end,
  step = step,
  batch_size = batch_size
)


###the model ###

model <- keras_model_sequential() %>%
  layer_lstm(units = 12, input_shape = list(NULL, dim(data)[[-1]]),return_sequences = T, dropout=0.2) %>%
  layer_lstm(units = 12, return_sequences = F, dropout = 0.2) %>%
  layer_dense(units = 6, activation = "selu") %>%
  layer_dense(units = 1, activation = "selu")

model %>% compile(optimizer = "adam",
                  loss= 'mse',
                  )
summary(model)
callbacks <- list(
  callback_early_stopping(patience = 10, monitor = 'val_loss',restore_best_weights=TRUE,min_delta = 0.001),
  callback_tensorboard(log_dir = './logs')
)
?callback_early_stopping
history <- model %>% fit(
  train_gen,
  steps_per_epoch = train_steps,
  epochs = 100,
  use_multiprocessing = T,
  validation_data = val_gen,
  validation_steps = val_steps,
  callbacks = callbacks

)

#### test set ###########
batch_size_plot = round(test_end-test_start-lookback)
  lookback_plot <- lookback
  step_plot <- 1 
  
  pred_gen <- generator(
    data,
    lookback = lookback,
    delay = 0,
    min_index = test_start,
    max_index = test_end,
    step = step_plot,
    batch_size = batch_size_plot
  )
  
 pred_gen_data <- pred_gen()
  
  V1 = seq(1, length(pred_gen_data[[2]]))
  
  plot_data <-
    as.data.frame(cbind(V1, pred_gen_data[[2]]))
  
  inputdata <- pred_gen_data[[1]][,,]
  dim(inputdata) <- c(batch_size_plot,lookback/step_plot,ncol(data))
  
  pred_out <- model %>%
    predict(inputdata) 


  plot_data <-
    cbind(plot_data, pred_out[])
  
  #add back dates
  plot_data$date <- index(dat_h)[(1+test_start):(test_start+nrow(pred_gen_data[[2]]))]
  plot_data <- as.xts(plot_data[,-4],order.by = plot_data[,4])
  colnames(plot_data)[3] <- "prediction"
  
  #decenter to get back original scale
   decenter <- function(x,std,mean) {
    return(x*std+mean)
   }
   plot_data$rv <- decenter(plot_data$V2,std_dat[1],mean_dat[1])
   plot_data$rv_pred <- decenter(plot_data$prediction,std_dat[1],mean_dat[1])
  autoplot(plot_data$rv)
  p <- ggplot(plot_data, aes(x = index(plot_data), y = rv)) + geom_line( colour = "blue", size = 0.2,alpha=0.3)
  p <- p + geom_point(aes(x = index(plot_data), y = rv_pred), colour = "red", size = 0.1 ,alpha=0.2) 
  p <- p + theme(panel.background = element_rect(fill = 'white', colour = 'black'))
  p <- p + labs(y = "RV", x = "Date") + ggtitle(paste0(curr," LSTM"))
  p
  ggsave(p, filename = paste0(path,"Plots/",curr,"_",t_period,"_",variab,"_LSTM.png"),height = 2, width = 9)  

  #rmse
  plot_data <- as.data.frame(plot_data)
  acc_tab <- data.frame(t(accuracy(plot_data$rv_pred,plot_data$rv)))
  print(acc_tab)
  tab_df(acc_tab,digits=4,show.rownames = T,col.header = c(curr),
         file = paste0(path,"Tables/",curr,"_",t_period,"_",variab,"_LSTM_acc_tab.doc"))
  
  df <- acc_tab
  colnames(df) <- curr
  df$Parameter <- rownames(df)
  df <- df[,c(2,1)] #change row order
  if (dim(df_all)[1] == 0){
  df_all <- df
  }else{
 df_all <- join(df_all,df,by="Parameter") 
  }

  #acc_tab$Parameter
  #acc_tab$variable <- toString(vars)
  #acc_tab$currency <- curr
  loss_p <- plot(history) + theme(panel.background = element_rect(fill = 'white', colour = 'black'))+ ggtitle(curr)
  ggsave(loss_p, filename = paste0(path,"Plots/","loss_plot",curr,"_",t_period,"_",variab,"_LSTM.png"),height = 2, width = 9)  
  
}

  tab_df(df_all,digits=4,show.rownames = F,col.header = c(curr))
  
  tab_df(df_all,digits=4,show.rownames = F,col.header = c(curr),
         file = paste0(path,"Tables/","all","_",t_period,"_",variab,"_LSTM_acc_tab.doc"))
  
```






